%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:

% Written by Rasmus
% \begin{comment}
% Because of their forensic value, system logs represent an obvious attack tar-
% get. An attacker who gains access to a system naturally wishes to remove traces
% of its presence in order to hide attack details or to frame innocent users. In fact,
% the first target of an experienced attacker is often the logging system [Bel-
% lare and Yee 1997; Bellare and Yee 2003]. To make the audit log secure, we
% must prevent the attacker from modifying log-data. Secure versions of audit
% logs should be designed to defend against such tampering. Providing integrity
% checks, the primary security requirement for any secure logging system, is in-
% formally stated in the Orange Book [U.S. Department of Defense 1985] as:
% Audit data must be protected from modification and unauthorized
% destruction to permit detection and after-the-fact investigation of
% security violations.
% In addition to the traditional meaning of data integrity which stipulates no
% insertion of fake data and no modification or deletion of existing data, integrity
% of a log file also requires no reordering of log entries. We call this property log
% stream integrity.
% In many real-world applications, a log file is generated and stored on a un-
% trusted logging machine that is not physically secure enough to guarantee im-
% possibility of compromise [Schneier and Kelsey 1998]. Compromise of a logging
% machine can happen as long as the Trusted Computing Base (TCB)—the system
% component responsible for logging—is not totally bug-free, which is unfortu-
% nately always the case. In systems using remote logging (which send audit data
% to a remote trusted server), if the server is not available, the log is buffered and
% stored temporarily at the local machine. Once an attacker obtains the secret
% key of the compromised logging machine, it can modify post-compromise data
% at will. In this case, one important issue is forward integrity: how to ensure
% that pre-compromise data cannot be manipulated? That is, the attacker who
% obtains the current secret key, must be unable to modify audit data generated
% before compromise.
% No security measure can protect log entries created after an attacker gains
% control of a logging machine, unless the logging machine’s keys are periodi-
% cally updated with the help of a remote trusted server or a local trusted hard-
% ware component (e.g., using key-insulated and intrusion-resilient authentica-
% tion schemes [Bellare and Palacio 2002; Dodis et al. 2002, 2003]). We focus
% on the security of log entries pre-dating the compromise of a logging machine.
% Consequently, we require forward-secure stream integrity, that is, resistance
% against post-compromise insertion, alteration, deletion and reordering of pre-
% compromise log entries.
% Traditional log integrity techniques involve using specialized write-only hard
% disks or remote logging whereby copies of log entries are sent to several geo-
% graphically distributed machines. With the former, disk substitution can result
% in a complete integrity compromise of the entire log. In the latter, the remote
% server may go offline (or become unreachable) and the logging machine then
% ACM Transactions on Storage, Vol. 5, No. 1, Article 2, Publication date: March 2009.A New Approach to Secure Logging
% has to locally buffer new log entries, which, in turn, become subject to attacks.
% Furthermore, if the remote server is compromised, log file integrity cannot be
% guaranteed.
% \end{comment}

When designing a secure system, you first have to identify what the
threats are and how likely they are to occur, in other words, the
risks. In this section we will analyze the threats to our system by
first considering the system's assets and how valuable they are. After
having identified what we need to protect, we will look into what
vulnerabilities our system would be exposed
to~\cite[p. 528]{pfleeger}. With the understanding of the assets and
vulnerabilities in our system we are able to look at the threats and
their respective likelihood. We will end the threat analysis by
considering attackers who would have a motive to attack our system.

\subsection{Assets}
As described in section~\ref{sec:intro}, our scenario describes a
system of servers emitting their log-data to a central logging
server. This is done with the intent, that by monitoring the stream of
log-data, the central server will be able to find signs of faults or
intrusions. Since we do not know exactly what servers from DTU that is
included in the system, we assume in this analysis that the system
includes all DTU's servers, such as the HPC'\footnote{DTU High
  Performance Computer. \url{http://www.hpc.dtu.dk/}} server park, the
servers hosting CampusNet\footnote{DTU
  CampusNet. \url{https://www.campusnet.dtu.dk/}}, etc.

We have several assets that makes up the system, which can be grouped
into the categories: Intellectual Properties, Documentation, Hardware,
Software and Data. Below we will outline how the assets of our system
falls into these categories.

\paragraph{Intellectual Property}
Due to our system belonging to an university, DTU, the servers in this
system will most likely contain state of the art research and research
results. Since the internal system, CampusNet, is hosted on DTU's
servers, assignments and handed-ins from students is an asset of the
system. The servers might also contain patents since DTU is known to
be the university in Denmark generating the most patents and
inventions. Since DTU is also commercializing these inventions they
will also have business secrets that might be found on some of the
servers~\footnote{\raggedright \url{
    http://ait-psc03cd05.win.dtu.dk/english/Collaboration/Industrial_Collaboration/Inventions-and-Patents}}.

\paragraph{Documentation}
One could think that the university would have manuals for specific
machines stored on the servers, as well as internal documentation for
procedures. Many of the courses at DTU also hosts course websites on
the servers, as well as researchers' websites.

\paragraph{Hardware}
Since the servers in the system are themselves of value, they are also
considered assets of the system.

\paragraph{Software}
DTU uses a range of different software, both licensed operating
systems and expensive scientific software, while also developing
software themselves. Much of this software could be installed and
distributed through servers at DTU.

\paragraph{Data}
The servers in the system will contain a lot of data. This data could
for example be the grades for students assignments as well as their
course grades. Essential to the problem scenario is also the log-data
emitted from different server on the network.

From the identified assets, the hardware and software assets can be
replaced, which would cost money. However the intellectual properties,
documentation and data are much harder to replace, since they are
unique and not an off-the-shelf asset.

\subsection{Vulnerabilities and threats}
We have considered the valuable assets in our system. We will now look
at the vulnerabilities of the identified assets. In order to look at
the vulnerabilities of the assets we use the C-I-A
triad~\footnote{AND73 in \cite{pfleeger}} to categorize the
vulnerabilities of the assets in terms of confidentiality,
availability and integrity. The confidentiality of a system is the
system’s ability to protect the sensitive data from unauthorized
access. The integrity of a system describes whether the data in the
system is trustworthy, and that it has not been modified with in an
unauthorized manner. The availability of a system is its ability to
ensure that an asset can be used by those who are allowed to use it.

In order to see what the vulnerabilities for the assets are in terms
of the C-I-A triad we see an overview in
table~\ref{tbl:vul-matrix}. If we look at the hardware assets of the
system, we would have vulnerabilities in terms of the integrity where
a threat could be that an attacker took control of the hardware
through a backdoor. Of course the hardware is also vulnerable for
being stolen or destroyed physically. In terms of the software in our
system this would like the hardware be vulnerable to a backdoor in the
code, which could be exploited by an attacker. The software would also
be vulnerable on the available if the license where expired or if an
attacker or simply a trusted part deleted the software by incident.

If we then look to the documentation assets these are not as
vulnerable on the confidentiality since the documentation might be
publicly available anyway, such as course information. However an
attacker could tamper with the documentation which would be a serious
threat as the integrity of the documentation is important. In terms of
availability an attacker could delete the documentation or launch a
denial of service attack compromising the availability.

Considering the intellectual properties, these assets are both
vulnerable in terms of their confidentiality, integrity and
availability. If we think of research results, it is very important
that these are confidential, since a researcher would might want to
publish his or hers academic results before other academics. In terms
of integrity it is important that the results are not tampered with so
that the researcher would not draw wrong conclusions. Also for other
intellectual properties, such as business plans and patents, the
confidentiality, integrity and availability is also important.

With the data assets it is essential to have complete integrity since
e.g. we want to be able to trust what the log says or that the student
grades are correct. We would also, in the case of grades, like to have
confidentiality in the asset that it is not available to the public
without permission from the student. Of course the data needs to be
available, otherwise the data would not be useful.

\begin{table}[h!]
  \centering
  \begin{tabular}{l|l|l|l}
    \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{\textbf{Confidentiality}} & \multicolumn{1}{c|}{\textbf{Integrity}} & \multicolumn{1}{c}{\textbf{Availability}} \\ \hline
    Intellectual Property & disclosure & tampered & stolen, destroyed \\ \hline
    Documentation & & tampered & destroyed, unavailable \\ \hline
    Hardware & & backdoor & stolen, destroyed \\ \hline
    Software & & backdoor & deleted, license expire \\ \hline
    Data & disclosure, inference & tampered & deleted, ransom ware
  \end{tabular}
  \caption{\label{tbl:vul-matrix} Vulnerability matrix}
\end{table}

\subsection{Attacker}
Some of the more valuable assets of our system would be the
intellectual properties, since this system belongs to a university,
where intellectual property are the basis for the
organization. Another important asset is the data, which in the case
of grading could be determining the students future career, and in the
terms of logs it is valuable for system administrators to monitor what
is going on in the system. Thus, we could think of the most likely
attacks would be against the intellectual property and the data, as
they have the most value.

The attackers of our system could be students who would like to change
their grade and thus attack the integrity of the data. These attackers
would go in the category of script kiddies, an adversary with little
knowledge or skill. Another attacker could be governments who would
not like to have some of the university's research to be published,
because it could destroy a political result and thus they would try to
tamper with some research or attack the availability of the
research. Other attackers would be companies who would like to gain
inside knowledge of business secrets or pending patents and they will
thus be a threat to the confidentiality or availability.

Common for these attackers is that whatever they do, a counter measure
from DTU's side would be to detect when any of the assets has been
attacked. One way of detecting these attacks is by logging the events
of the server to a central server. This makes the log-data a common
target for all the attackers and the log-data would be vulnerable. The
attackers would like to attack the integrity of the log by tampering
with the content of the log, as deleting the log in its entirety would
easily be noticed.

\subsection{Scope of our project}
In this project we are focusing mainly on the log-data asset. Since
this asset is a common target for all the attacker models it is of
paramount importance that it is well protected. Since it is a premise
for the system that the servers are insecure, we are considering the
integrity of the log-data on the central server. It is important that
the log-data is forward-secure such that it is not possible to tamper
with already logged events. We will thus be focusing on designing a
cryptographic countermeasure against attack on the integrity of the
main server log and not on the integrity of the logging events from
the servers that might have been hijacked by an attacker.


% \begin{comment}
% Basic Steps
% \begin{enumerate}
%     \item Identify assets
%     \item Determine vulnerabilities
%     \item Estimate likelihood of exploitation
%     \item Calculate consequences (typically as expected annual loss)
%     \item Survey applicable controls and their costs
%     \item Project annual savings of control
% \end{enumerate}

% \subsection{Identify assets}
% Logdata

% \subsection{Determine vulnerabilities}
% \begin{table}[h!]
% \centering
% \caption{My caption}
% \label{my-label}
% \begin{tabular}{l|l|l|l}
% \multicolumn{1}{c|}{} & \multicolumn{1}{c|}{Confidentiality} & \multicolumn{1}{c|}{Integrity} & \multicolumn{1}{c}{Availability} \\ \hline
% Hardware              &                                      & tampered                       & stolen, destroyed                \\ \hline
% Software              &                                      & backdoor                       & deleted, license expire          \\ \hline
% Data                  & disclosure, inference                & tampered                       & deleted, ransom ware
% \end{tabular}
% \end{table}
% \subsection{Estimate likelihood of exploitation}
% Software backdoor

% Data disclosure

% \subsection{Calculate consequences (typically as expected annual loss)}
% \subsection{Survey applicable controls and their costs}
% \subsection{Project annual savings of control}
% \end{comment}
